\begin{thebibliography}{9}
		\bibitem{doremus} DOREMUS: DOing REusable MUSical data. | \textit{\href{http://www.doremus.org/}{http://www.doremus.org/}}
		\bibitem{bobrow} Natural Language Input for a Computer Problem Solving System. 1964. Bobrow, Daniel. | \textit{\href{http://dspace.mit.edu/handle/1721.1/5922}{http://dspace.mit.edu/handle/1721.1/5922}}
		\bibitem{eliza} ELIZA: A computer program for the study of natural language communication between man and machine. 1966. Weizenbaum, Joseph. | \textit{\href{https://dl.acm.org/citation.cfm?id=365168}{https://dl.acm.org/citation.cfm?id=365168}}
		\bibitem{woods} Augmented Transition Networks for Natural Language Analysis. 1969. Woods, William. | \textit{\href{https://eric.ed.gov/?id=ED037733}{https://eric.ed.gov/?id=ED037733}}
		\bibitem{nlpnlunlg} NLP, NLU, NLG and how Chatbots work. | \textit{\href{https://chatbotslife.com/nlp-nlu-nlg-and-how-chatbots-work-dd7861dfc9df}{https://chatbotslife.com/nlp-nlu-nlg-and-how-chatbots-work-dd7861dfc9df}}
		\bibitem{rnn} Attention-Based Recurrent Neural Network Models for Joint Intent Detection and Slot Filling. 2016. Liu, Bing and Lane, Ian. | \textit{\href{https://arxiv.org/abs/1609.01454}{https://arxiv.org/abs/1609.01454}}
		\bibitem{unified} A Unified Architecture for Natural Language Processing: Deep Neural Networks with Multitask Learning. 2008. Collobert, Ronan and Weston, Jason. | \textit{\href{https://ronan.collobert.com/pub/matos/2008\_nlp\_icml.pdf}{https://ronan.collobert.com/pub/matos/2008\_nlp\_icml.pdf}}
		\bibitem{dialogflow} Dialogflow: Build natural and rich conversational experiences. | \textit{\href{https://dialogflow.com/}{https://dialogflow.com/}}
		\bibitem{witai} Wit.ai: Turn what your users say into actions. | \textit{\href{https://wit.ai/}{https://wit.ai/}}
		\bibitem{snips} Snips: Using Voice to Make Technology Disappear. | \textit{\href{https://snips.ai/}{https://snips.ai/}} | \textit{\href{https://github.com/snipsco}{https://github.com/snipsco}}
		\bibitem{watson} IBM Watson: Does your business think? | \textit{\href{https://www.ibm.com/watson/}{https://www.ibm.com/watson/}}
		\bibitem{lex} Amazon Lex: Build conversation bots. | \textit{\href{https://aws.amazon.com/lex/}{https://aws.amazon.com/lex/}}
		\bibitem{luis} Microsoft LUIS: A machine learning-based service to build natural language into apps, bots, and IoT devices. | \textit{\href{https://www.luis.ai/}{https://www.luis.ai/}}
		\bibitem{recast} SAP Recast.ai: A collaborative bot platform. | \textit{\href{https://recast.ai/}{https://recast.ai/}}
		\bibitem{apiai} Chatbots made easy with Dialogflow. An overview on the architecture. | \textit{\href{https://blog.huhtanen.eu/2017/10/15/chatbots-made-easy-dialog-flow.html}{https://blog.huhtanen.eu/2017/10/15/chatbots-made-easy-dialog-flow.html}}
		\bibitem{bmd} The GitHub repository of the Botkit middleware for Dialogflow. | \textit{\href{https://github.com/jschnurr/botkit-middleware-dialogflow}{https://github.com/jschnurr/botkit-middleware-dialogflow}}
		\bibitem{pr1} First pull request: "Added capability to change language in Dialogflow" | \textit{\href{https://github.com/jschnurr/botkit-middleware-dialogflow/pull/10}{https://github.com/jschnurr/botkit-middleware-dialogflow/pull/10}}
		\bibitem{pr2} Second pull request: "The sessionID is set to message.user, to have a separate session for each user" | \textit{\href{https://github.com/jschnurr/botkit-middleware-dialogflow/pull/11}{https://github.com/jschnurr/botkit-middleware-dialogflow/pull/11}}
		\bibitem{fade} FADE: Filling Automatically Dialog Entities | \textit{\href{https://github.com/marcotrinelli/FADE}{https://github.com/marcotrinelli/FADE}}
	\end{thebibliography}